Experience-Biased Symbolic Planning

### 2014-05-14 AAAI_AuthorKit/paper.tex
predinner version

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA} \and Maxim Likhachev% <-this % stops a space
\thanks{Carnegie Mellon University, Pittsburgh, PA.
We thank Willow Garage for their support of this work. This research was also sponsored by ARL, under the Robotics CTA program grant W911NF-10-2-0016.}% <-this % stops a space
%
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP2 by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

Alot of symbolic planners that have emerged in recent years are based on forward weighted A* search. This paper focuses on HSP2 as a representative example, because it is fairly simple and embodies the core ideas common to many state-of-the-art planners. The use of E-graphs is orthogonal to many of the latest improvements, so our methods can in principle be adapted to any A* planner.

@@

\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$. $h$ is \textbf{consistent} if it is $1$-consistent. \end{defn}
\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost. [CITE ARA*] \end{thm}

@@

\begin{center}
\includegraphics[scale=0.5]{Pentagon.png}
\end{center}

The above figure illustrates the idea. Suppose the dark edges have cost 3 and make up the E-graph. Off-E-graph edges are not shown, as they are only accessed indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively). Dijkstra's algorithm follows dark and light edges backward to compute the $h^E$ values shown alongside each node.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA 90089} \and Maxim Likhachev% <-this % stops a space
\thanks{Carnegie Mellon University, Pittsburgh, PA 15217}% <-this % stops a space
%
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP2 by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

A lot of symbolic planners that have emerged in recent years are based on forward weighted A* search. This paper focuses on HSP2 as a representative example, because it is fairly simple and embodies the core ideas common to many state-of-the-art planners. The use of E-graphs is orthogonal to many of the latest improvements, so our methods can in principle be adapted to any A* planner.

@@

\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$. $h$ is \textbf{consistent} if it is $1$-consistent. \end{defn}
\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}. \end{thm}

@@

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Pentagon.png}
	\end{center}
	\caption{An example E-graph and corresponding heuristic computations.}
	\label{fig:example}
\end{figure}

Figure \ref{fig:example} illustrates the idea. Suppose the dark edges have cost 3 and make up the E-graph. Off-E-graph edges are not shown, as they are only accessed indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively). Dijkstra's algorithm follows dark and light edges backward to compute the $h^E$ values shown alongside each node.
